---
title: "NAME"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NAME}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(automater)
automater::validate_package("")
```


... using () function.

```{r eval = FALSE}

```

To run () automatically, use ....rsc in rsc directory within automater package.

- Save ....rsc to a directory.    
  You can copy ....rsc by code below.    

```{r eval = FALSE}
rsc <- system.file("rsc/....rsc", package = "automater")
target_dir <- "c:/" # set your directory
file.copy(rsc, target_dir)
```

- Associate extension .rsc with Rscript.exe.    
  https://www.computerhope.com/issues/ch000572.htm    


- Copy excel files to the same directory with ....rsc.   
- Click ....rsc.   
- Then a black command windows will be opened and wait a moment.   
- At the first time to run ....rsc, browser stars and ask for your ID and password for authorization.   
- Input ID and password, then you will be authorized.    
- After authorization, close browser.   

If you want not to send emails but only make draft, 


Contents of ....rsc is shown below. 

```{r}
rsc <- system.file("rsc/....rsc", package = "automater")
cat(readtext::readtext(rsc, verbosity = 0)$text)
```
