---
title: "a"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(automater)
automater::validate_package("xlsx")
```


Set autofilter and freeze panel of all excel files (xls and xlsx) in a directory using set_af_fp() function.

```{r eval = FALSE}
files <- list.files(pattern = "xls")
for(file in files){
  automater::set_af_fp(file)
}
```

To run set_af_fp() automatically, use set_autofilter_freezepanel.rsc in rsc directory within automater package.

- Save set_autofilter_freezepanel.rsc to a directory.    
  You can copy set_autofilter_freezepanel.rsc by code below.    

```{r eval = FALSE}
rsc <- system.file("rsc/set_autofilter_freezepanel.rsc", package = "automater")
target_dir <- "c:/" # set your directory
file.copy(rsc, target_dir)
```

- Associate extension .rsc with Rscript.exe.    
  https://www.computerhope.com/issues/ch000572.htm    

- Copy excel files to the same directory with set_autofilter_freezepanel.rsc.   
- Click set_autofilter_freezepanel.rsc.   
- Then a black command windows will be opened and wait a moment.   

Contents of set_autofilter_freezepanel.rsc is shown below. 
