---
title: "Combine pdf with qpdf"
output: 
  html_document:
    keep_md: true
  # output: rmarkdown::html_vignette
  # vignette: >
  #   %\VignetteIndexEntry{Combine pdf with qpdf}
  #   %\VignetteEngine{knitr::rmarkdown}
  #   %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(automater)
automater::validate_package("qpdf")
```


Combine pdf with qpdf using qpdf::pdf_combine() function.
This function combine several pdf files into one.


```{r eval = FALSE}
files <- c("a.pdf", "b.pdf", "c.pdf")
qpdf::pdf_combine(files)
```

To run () automatically, use combine_qpdf.rsc in rsc directory within automater package.   

- Save combine_qpdf.rsc to a directory.    
  You can set combine_qpdf.rsc by code below.    

```{r eval = FALSE}
file <- "combine_qpdf"
path <- "c:/" # set your path
automater::set_rsc(file, path)
```

- On Windows Associate extension .rsc with Rscript.exe.    
  https://www.computerhope.com/issues/ch000572.htm    


- Copy PDF files to the same directory with combine_qpdf.rsc.   
- Click combine_qpdf.rsc.   
- Then a black command window will be opened and wait a moment.   
- At the first time to run combine_qpdf.rsc, it may take few minutes to install packages.   
- The order to combined files is the same with the order of the file names.    
  You need to rename files before using combine_qpdf.rsc.    
- The output file is name will be like "combined_"2020-11-27_12_00_00.pdf".    

Contents of combine_qpdf.rsc is shown below. 

```{r}
rsc <- system.file("rsc/combine_qpdf.rsc", package = "automater")
cat(readtext::readtext(rsc, verbosity = 0)$text)
```
