---
title: "ocr with tesseract"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ocr_tesseract}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(automater)
automater::validate_package("tesseract")
```


COR (Optical Character Recognition, extract text from image files) with package tesseract. 

```{r eval = FALSE}
files <- list.files(pattern = "bmp|gif|png|tif|tiff")
text <- list()
for(file in files){
  text[file] <- automater::ocr_tesseract(file)
}
text
```


To run automater::ocr_tesseract() automatically and save contents into text files, 
use orc_tesseract.rsc in rsc directory within automater package.
When image file name is "image.png", text file will be "image.png.txt" 

- Save orc_tesseract.rsc to a directory.    
  You can copy orc_tesseract.rsc by code below.    

```{r eval = FALSE}
rsc <- system.file("rsc/orc_tesseract.rsc", package = "automater")
target_dir <- "c:/" # set your directory
file.copy(rsc, target_dir)
```

- Associate extension .rsc with Rscript.exe.    
  https://www.computerhope.com/issues/ch000572.htm    

<!--
  # assoc .rsc=rscript
  # ftype rscript="D:\pf\R\R-4.2.3\bin\x64\Rscript.exe" "%1"
  # file.path(R.home(), "bin", "x64", "Rscript.exe")
  # assoc .rsc
  # ftype rscript
-->

- Copy image files (bmp, gif, png, tif, tiff) to the same directory with orc_tesseract.rsc.   
- Click orc_tesseract.rsc.   
- Then a black command windows will be opened and wait a moment.   

Contents of orc_tesseract.rsc is shown below. 

```{r}
rsc <- system.file("rsc/orc_tesseract.rsc", package = "automater")
cat(readtext::readtext(rsc, verbosity = 0)$text)
```
