---
title: "NAME"
output: 
  html_document:
    keep_md: true
  # output: rmarkdown::html_vignette
  # vignette: >
  #   %\VignetteIndexEntry{NAME}
  #   %\VignetteEngine{knitr::rmarkdown}
  #   %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(automater)
automater::validate_package("")
```


... using () function.


```{r eval = FALSE}

```


To run () automatically, use ***.rsc in rsc directory within automater package.   

- Save ***.rsc (and ***.command, then chmod ***.command "755" on Mac) to a directory.    
  You can set ***.rsc (and ***.command on Mac) by code below.    

```{r eval = FALSE}
file <- "***"
path <- "c:/" # set your path
automater::set_rsc(file, path)
```

- On Windows Associate extension .rsc with Rscript.exe.    
  https://www.computerhope.com/issues/ch000572.htm    


- Copy ... files to the same directory with ***.rsc.   
- Click ***.rsc on Windows (***.command on Mac).   
- Then a black command windows will be opened and wait a moment.   
- At the first time to run ***.rsc, it may take few minutes to install packages.   


Contents of ***.rsc is shown below. 

```{r}
  # rsc <- system.file("rsc/....rsc", package = "automater")
  # cat(readtext::readtext(rsc, verbosity = 0)$text)
```
