---
title: "Split pdf with qpdf"
output: 
  html_document:
    keep_md: true
  # output: rmarkdown::html_vignette
  # vignette: >
  #   %\VignetteIndexEntry{Split pdf with qpdf}
  #   %\VignetteEngine{knitr::rmarkdown}
  #   %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(automater)
automater::validate_package("qpdf")
```


Split pdf with qpdf using qpdf::pdf_split() function.
This function split a single pdf file into separate files, one for each page. 

```{r eval = FALSE}
qpdf::pdf_split("a.pdf")
```

To run () automatically, use split_qpdf.rsc in rsc directory within automater package.   

- Save split_qpdf.rsc to a directory.    
  You can set split_qpdf.rsc by code below.    

```{r eval = FALSE}
file <- "split_qpdf"
path <- "c:/" # set your path
automater::set_rsc(file, path)
```

- On Windows Associate extension .rsc with Rscript.exe.    
  https://www.computerhope.com/issues/ch000572.htm    


- Copy PDF files to the same directory with split_qpdf.rsc.   
- Click split_qpdf.rsc.   
- Then a black command window will be opened and wait a moment.   
- At the first time to run split_qpdf.rsc, it may take few minutes to install packages.   
- The output file is like as below.    
  - input: "original.pdf" (including 15 pages)
  - output: "original_01.pdf", "original_02.pdf", ..., "original_15.pdf"

Contents of split_qpdf.rsc is shown below. 

```{r}
rsc <- system.file("rsc/split_qpdf.rsc", package = "automater")
cat(readtext::readtext(rsc, verbosity = 0)$text)
```
