---
title: "translate with deeplr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{translate_deeplr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(automater)
automater::validate_package("deeplr")
automater::validate_package("dplyr")
```


Translate with package deeplr. 

```{r eval = FALSE}
api_key <- "set_your_key"
  # Example: from "I am a cat" by Soseki Natsume
sentences <- c("I am a cat. I don't have a name yet.", 
               "I have no idea where I was born.")
tibble::tibble(en = sentences) %>%
  dplyr::mutate(`:=`("jp", deepl_api(en, api_key = api_key)))
}
```

Read files, translate, and write them. 

```{r eval = FALSE}
api_key <- "set_your_key"
files <- list.files(pattern = "\\.txt")
for(file in files){
  txt <- utils::read.table(file, sep = "\t", col.names = "en")
  txt <- dplyr::mutate(txt, `:=`("jp", deepl_api(str = en, api_key = api_key)))
  utils::write.table(txt, paste0("translated_", file), quote = FALSE, sep = "\t", row.names = FALSE)
}
```


To run automater::deepl_api() automatically and save contents into text files, 
use translate_deeplr.rsc in rsc directory within automater package.
When input file name is "neko.txt", output file will be "translated_neko.txt" 

- Save translate_deeplr.rsc to a directory.    
  You can copy translate_deeplr.rsc by code below.    

```{r eval = FALSE}
rsc <- system.file("rsc/translate_deeplr.rsc", package = "automater")
target_dir <- "c:/" # set your directory
file.copy(rsc, target_dir)
```

- Associate extension .rsc with Rscript.exe.    
  https://www.computerhope.com/issues/ch000572.htm    
- Set your deepl api key in translate_deeplr.rsc (required).    
  api_key <- "set_your_key"   
- Copy text files (*.txt) to the same directory with translate_deeplr.rsc.   
- Click translate_deeplr.rsc.   
- Then a black command windows will be opened and wait a moment.   

Contents of translate_deeplr.rsc is shown below. 

```{r}
rsc <- system.file("rsc/translate_deeplr.rsc", package = "automater")
cat(readtext::readtext(rsc, verbosity = 0)$text)
```
